ONE ARABESQUE IN THE SMALL WORLD OF OD WEBMAPS

### 2021-07-29 presentations/FOSS4G2021_presentation.Rmd
Add more details

---
title: "ONE ARABESQUE IN THE SMALL WORLD OF OD WEBMAPS"
subtitle: "FOSS4G 2021"  
author: 
  - "Nicolas Roelandt"
date: '`r Sys.Date()`'
output:
  xaringan::moon_reader:
    seal: false
    css: ["xaringan-themer.css", "custom.css"]
    nature:
      slideNumberFormat: "%current%"
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: true
---
```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.width=9, fig.height=3.5, fig.retina=3,
  out.width = "100%",
  cache = FALSE,
  echo = TRUE,
  message = FALSE, 
  warning = FALSE,
  hiline = TRUE
)
```

>>>>

---
title: "ONE ARABESQUE IN THE SMALL WORLD OF OD WEBMAPS"
subtitle: "FOSS4G 2021"  
author: 
  - "Nicolas Roelandt"
date: '`r Sys.Date()`'
output:
  xaringan::moon_reader:
    self_contained: true
    seal: false
    css: ["xaringan-themer.css", "custom.css"]
    nature:
      slideNumberFormat: "%current%"
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: true
---
```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.width=9, fig.height=3.5, fig.retina=3,
  out.width = "100%",
  cache = FALSE,
  echo = TRUE,
  message = FALSE, 
  warning = FALSE,
  hiline = TRUE
)
```
